### 2021-02-23 architecture.tex
Graph constructor > Graphifier
Jelle found the word "graphifier" confusing.

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: Graphifier converts the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
Ale v te prislusne podsekci tim zas zacit.}
\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{itemize}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}

@@

Problem [label="CNF problem P"];
Graphifier [style=rounded, label="Graphifier"];
g [label="Graph"];
GCN [style=rounded, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=rounded, label="Projection"];
SymbolCost [label="Symbol costs"];
Sort [style=rounded, label="Sort"];
Precedence [label=<Output precedence &pi;*>];

>>>>

The recommender consists of modules that perform specific subtasks,
each of which is described in detail in one of the following sections (see also \cref{fig:architecture}):
\begin{itemize}
\item \Cref{sec:graphifier}: A graph constructor converts the input \gls{cnf} problem into a problem graph.
\item \Cref{sec:gcn}: \Gls{gcn} converts a problem graph into symbol embeddings.
\todo{MS: Kdyz embeddingy nebudou v preliminaries, je asi OK ctenare, ktery by o nich neslysel, zde trochu vydesit.
Ale v te prislusne podsekci tim zas zacit.}
\item \Cref{sec:output}: An output function \cite{Zhou2018} converts the symbol embeddings into a vector of symbol costs.
\todo{MS: ``output function \cite{Zhou2018}'' my nic nerika, mel bych to znat?\\
FB: Zhou2018 je review GNNs. Output function je termin, ktery se tam pouziva. Ta citace je nejspis tady nepotrebna.}
\item \Cref{sec:ranking}: Sorting converts the symbol costs into a symbol precedence.
It is only used in generating mode.
\item \Cref{sec:training}: Loss function converts the symbol costs and a pair of precedences into a loss value.
It is only used in training mode.
\end{itemize}
\todo{MS: tohle zatim chapu jako predbezny nastrel. Leda by uz pred tim bylo vysvetleno:
embedding, \gls{gcn}/convolution layers, ... \\
FB: Staci predestrit, ze detaily vysvetlim pozdeji? MS: asi jo :)}

@@

Problem [label="CNF problem P"];
Graphifier [style=rounded, label="Graph constructor"];
g [label="Graph"];
GCN [style=rounded, label="GCN"];
SymbolEmbedding [label="Symbol embeddings"];
SymbolCostModel [style=rounded, label="Projection"];
SymbolCost [label="Symbol costs"];
Sort [style=rounded, label="Sort"];
Precedence [label=<Output precedence &pi;*>];
